Radio Emission from Red-Giant Hot Jupiters

### 2015-12-29 ms.tex
typo corrected

Let us also consider the expected number of radio detection from RGHJs taking account of the occurrence rate of Jovian planets. 
For this purpose, we consider an empirical power-law planet occurrence rate described as
%%%
\begin{eqnarray}
f(M_p,P) &\equiv & \frac{d^2N}{d\log M_pd\log P } \\
&=& \mathcal{C} \left( \frac{M_p}{M_{\rm J}} \right)^{\alpha } \left( \frac{P}{1~{\rm days}} \right)^{\beta }
\end{eqnarray}
%%%
where \citet{cumming2008} found $\alpha = -0.31\pm 0.2$, $\beta =0.26 \pm 0.1$, $\mathcal{C} =1.04\times 10^{-3}$  as best-fit values. %
Using this equation, the probability of a given evolved star in Figure \ref{fig:observability} to have a RGHJ with mass larger than threshold $M_{p0}$ whose radio emission may be detectable is
%%%
\begin{equation}
\mathcal{P }(>M_{p0}) \sim \int_{M_{p0}} d\log M_p\,\int_{P_{\rm min}(M_p)}^{P_{\rm max}(M_p)} d\log P ~f(M_p, P) \label{eq:detect_prob}
\end{equation}
%%%
where $P_{\rm min}(M_p)$ is the minimum orbital period to have cyclotron frequency larger than the ambient plasma frequency, while $P_{\rm max}(M_p)$ is the maximum orbital period given planetary mass to emit detectable radio flux. For the former, combining equations (\ref{eq:fcyc}) and (\ref{eq:fplasma_RG}) leads to
%%%
\begin{eqnarray}
a_{\rm min} (M_p) &=& 2.15~{\rm AU} \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04} \left( \frac{t}{4.5~{\rm Gyr}} \right)^{0.43}  \\
&&\times \left( \frac{\dot M_{\star }}{10^{-8}M_{\odot}/{\rm yr}} \right)^{1/2} 
\end{eqnarray}
%%%
while for the latter, equations (\ref{eq:scalingB}) and (\ref
{eq:F_nu_RGHJ}) indicate
%%%
\begin{eqnarray}
a_{\rm max} (M_p) &=& 3.80~{\rm AU} \left( \frac{F_{\rm min}}{10~\mu {\rm Jy}} \right)^
{-3/4} \left( \frac{d}{100~{\rm pc}} \right)^{-3/2} \\
&& \times \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04/4}  \left( \frac{t}{4.5~{\rm Gyr}} \right)^{-0.43/4} \\
&& \times \left( \frac{\dot M_{\star }}{10^{-8}M_{\odot }/{\rm yr}} \right)^{1/2} \left( \frac{v_{\star }}{10^{-1} v_{\odot }} \right)^{5/4} 
\end{eqnarray}
%%%
They are translated into the orbital period via Kepler's law, $P_{\{{\rm min,max}\}} = 2\pi \sqrt{a^3_{\{{\rm min,max}\}} / GM_{\star } }$.

@@

Using equation (\ref{eq:detect_prob}), the expected number for $M_p > >M_{p0}$ planet with detectable radio emission is $\sum _i \mathcal{P} _i(>M_{p0})$, where $\mathcal{P}_i(>M_{p0})$ is the probability for the $i$-th target.

>>>>

Let us also consider the expected number of radio detection from RGHJs taking account of the occurrence rate of Jovian planets. 
For this purpose, we consider an empirical power-law planet occurrence rate described as
%%%
\begin{eqnarray}
f(M_p,P) &\equiv & \frac{d^2N}{d\log M_pd\log P } \\
&=& \mathcal{C} \left( \frac{M_p}{M_{\rm J}} \right)^{\alpha } \left( \frac{P}{1~{\rm days}} \right)^{\beta }
\end{eqnarray}
%%%
where \citet{cumming2008} found $\alpha = -0.31\pm 0.2$, $\beta =0.26 \pm 0.1$, $\mathcal{C} =1.04\times 10^{-3}$  as best-fit values. %
Using this equation, the probability of a given evolved star in Figure \ref{fig:observability} to have a RGHJ with mass larger than threshold $M_{p0}$ whose radio emission may be detectable is
%%%
\begin{equation}
\mathcal{P }(>M_{p0}) \sim \int_{M_{p0}} d\log M_p\,\int_{P_{\rm min}(M_p)}^{P_{\rm max}(M_p)} d\log P ~f(M_p, P) \label{eq:detect_prob}
\end{equation}
%%%
where $P_{\rm min}(M_p)$ is the minimum orbital period to have cyclotron frequency larger than the ambient plasma frequency, while $P_{\rm max}(M_p)$ is the maximum orbital period given planetary mass to emit detectable radio flux. For the former, combining equations (\ref{eq:fcyc}), (\ref{eq:scalingB}), and (\ref{eq:fplasma_RG}) leads to
%%%
\begin{eqnarray}
a_{\rm min} (M_p) &=& 2.1~{\rm AU} \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04} \left( \frac{t}{4.5~{\rm Gyr}} \right)^{0.43}  \\
&&\times \left( \frac{\dot M_{\star }}{10^{-8}M_{\odot}/{\rm yr}} \right)^{1/2} 
\end{eqnarray}
%%%
while for the latter, equations (\ref{eq:scalingB}) and (\ref
{eq:F_nu_RGHJ}) indicate
%%%
\begin{eqnarray}
a_{\rm max} (M_p) &=& 3.8~{\rm AU} \left( \frac{F_{\rm min}}{10~\mu {\rm Jy}} \right)^
{-3/4} \left( \frac{d}{100~{\rm pc}} \right)^{-3/2} \\
&& \times \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04/4}  \left( \frac{t}{4.5~{\rm Gyr}} \right)^{0.43/4} \\
&& \times \left( \frac{\dot M_{\star }}{10^{-8}M_{\odot }/{\rm yr}} \right)^{1/2} \left( \frac{v_{\star }}{10^{-1} v_{\odot }} \right)^{5/4} 
\end{eqnarray}
%%%
They are translated into the orbital period via Kepler's law, $P_{\{{\rm min,max}\}} = 2\pi \sqrt{a^3_{\{{\rm min,max}\}} / GM_{\star } }$.

@@

Using equation (\ref{eq:detect_prob}), the expected number for planets more massive than $M_{p0}$ with detectable radio emission is $\sum _i \mathcal{P} _i(>M_{p0})$, where $\mathcal{P}_i(>M_{p0})$ is the probability for the $i$-th target.
